Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2025-06-01 src/docs_paper-jtb/revisions.Rmd
Almost there!

> Questions about the HIV model

Jeff broadly agrees with the reviewer.
(This is an area of current work on Naomi extension.)

@@

We agree that there are too many colours here for this figure to be clear, and that the suggestion to split the figure across panels is a good one.
To do so, we have grouped the parameters by the model component (e.g. HIV prevalence), and used colour to represent the type of parameter (e.g. intecept).

>>>>

> On the proportion recently infected and ANC offsets

Some HIV surveys provide bio-marker data on whether or not the infection was recent.
The equation in the manuscript links the probability of recent infection to HIV prevalence, HIV incidence, and properties of the recent infection assay.
This allows us to back-out estimates of the HIV incidence.
<!-- Is there something to add to the manuscript here? -->

We agree that tightening the bounds on the ANC offsets would be an important step for improving estimates of HIV incidence.
Work is ongoing to improve the Naomi model [@esra2024improved].
<!-- Has this work been included yet, or it's still to be done in future? -->

@@

We agree that there are too many colours here for this figure to be clear, and that the suggestion to split the figure across panels is a good one.
To do so, we have grouped the parameters by the model component (e.g. HIV prevalence), and used colour to represent the type of parameter (e.g. intercept).

### 2025-06-01 src/naomi-simple_ks/ks.Rmd
Almost there!

fct_reorg <- function(fac, ...) {
  fct_recode(fct_relevel(fac, ...), ...)
}

ks_df %>%
  filter(type != "Hyper") %>%
  mutate(method = fct_reorg(method, "GEB" = "TMB", "GPCA-AGHQ" = "aghq")) %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(shape = 1, alpha = 0.5) +
    geom_smooth(method = "lm", color = "#CC79A7", fullrange = TRUE) +
    ggpmisc::stat_poly_eq(ggpmisc::use_label("eq"), label.x.npc = "right") +
    ggpmisc::stat_poly_eq(label.y = 0.9, label.x.npc = "right") +
    scale_x_continuous(limits = c(0, NA)) +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "NUTS ESS", y = "KS(approach, NUTS)")

>>>>

ks_df %>%
  filter(type != "Hyper") %>%
  mutate(
    method = fct_recode(
      method,
      "GEB" = "TMB",
      "GPCA-AGHQ" = "aghq",
    ),
    method = fct_relevel(method, "GEB", "GPCA-AGHQ")
  ) %>%
  left_join(data.frame(ess) %>%
    tibble::rownames_to_column("par"),
  ) %>%
  ggplot(aes(x = ess, y = ks)) +
    geom_point(shape = 1, alpha = 0.5) +
    geom_smooth(method = "lm", color = "#CC79A7", fullrange = TRUE) +
    ggpmisc::stat_poly_eq(ggpmisc::use_label("eq"), label.x.npc = "right") +
    ggpmisc::stat_poly_eq(label.y = 0.9, label.x.npc = "right") +
    scale_x_continuous(limits = c(0, NA)) +
    facet_grid(~ method) +
    theme_minimal() +
    labs(x = "NUTS ESS", y = "KS(approach, NUTS)")
